\section{Introduction}
\label{s:intro}


Recent years have seen an immense growth in the number of wireless devices in use. Functionality of these devices has similarly evolved as one can find a mobile application for just about any task. In turn, the need for efficient and widespread wireless network coverage is at a high. However, today, customers are often susceptible to poor network coverage over both WiFi and cellular networks. Application developers find it difficult to understand how to optimize their application performance for different devices over wireless networks. Researchers struggle to find data to test potential improvements in wireless network and device performance. This arises from a lack of information about the behavior and performance of wireless networks for different devices, locations, and times. 

This work describes the design, implementation, and experimental evaluation of NetMap, a system that provides a battery-aware network performance measurement collection service with a simple API for mobile devices. Our main contributions are a measurement collection API designed for games as well as a packaging mechanism to collect performance data in a mobile device game. 

Our API provides a means to collect various types of data including user-specific data such as device model and location (GPS), network performance data including latency, bandwidth, and average round-trip-time, and neighboring network infrastructure information such as neighboring network type and signal strength to neighboring towers/access points. It is specifically designed for mobile device games. Game development is straightforward, as designers are not required to know how our measurements are collected, processed, stored, etc. Game designers simply use functions in our API to collect the requested data.

We developed a scheme which aligns incentives so game players collect measurements while playing. That is, we tie measurement collection at real-world locations with movement and action in the mobile device game. Ideally, the provided measurement library would be called upon when a game player moves (reflecting movement in real-life and consequently movement in-game). Measurement collection can thus be widespread as users provide measurements from various locations while playing their mobile device game.

Users of these mobile games are aware that they will be collecting information on network connectivity that will be used for research purposes. However, beyond providing permission, gameplay is the user¡¦s sole focus, as no additional effort must be expended to gather, store, or analyze the network performance measurements. We are also battery-aware so battery-intensive data collection and transfers are done only when battery permits reducing user overhead. 

Targeted results of using NetMap and a mobile device game are a collection of various network performance statistics such as bandwidth, latency, average round-trip-time, etc., user statistics such as phone models and battery, and a comprehensive map of how different wireless networks behave across various regions. From these results, researchers and game developers can infer cellular network and WiFi performance for different areas, devices, and times. Additionally, this will provide a reliable and up-to-date source of data for researchers to use in developing improvements for wireless and mobile device connectivity. 

The remainder of this paper is organized as follows¡K

