\subsection{Algorithm}
\label{ss:algorithm}
From the large amount of data we collect, we can infer several characteristics of 
wireless networks and their infrastructures. One such characteristic is the location 
of cell towers that users either connect to or are in the vicinity of, since we collect 
neighboring cell tower information. We tried two different algorithms for cell tower 
positioning which are described below. Each algorithm uses multiple readings to 
position a given cell tower. For each algorithm, we use the following abbreviations: \newline
L = Location of user \newline
T = Location of cell tower \newline
d = L - T = Distance from user to tower \newline
s = Signal strength of current reading \newline
stot = Sum of signal strengths from readings above threshold

{\bfseries Algorithm 1: Channel Model Estimation.}
We begin with the common model for wireless network channels: $s \propto \frac{k}{d^2}$
where k is the channel condition parameter. However, we don't know the channel 
condition parameter and it is difficult to accurately estimate. We do know that readings 
in similar locations should have similar channel condition parameters so we disregard 
k (since it is roughly constant across readings in same location at similar time) and state:

$d^2 = \frac{1}{s} \rightarrow d = \sqrt{\frac{1}{s}} \rightarrow L - T = \sqrt{\frac{1}{s}} \rightarrow T = L - \sqrt{\frac{1}{s}}$

To obtain cell tower location, we solve for T in each reading and use the location which solves 
$min(sd^2 – 1)$, which is derived from minimizing $d^2 = \frac{1}{s}$ (so $sd^2$ - 1 $\approx 0)$


{\bfseries Algorithm 2: Weighted Average of User Locations.}
We assume that users who connect or detect a cell tower with reasonable signal strength 
are relatively close to the tower. Since all user locations, after eliminating outliers, will be 
a small distance from the cell tower, and each will have a different orientation with respect 
to the cell tower, we weight each reading by signal strength and sum the locations to obtain 
an estimate of the cell tower location. 

We first, for all entries, eliminate those with signal strength below a threshold. This eliminates 
the use of outliers since very low signal strength implies that the user is not very close to the 
cell tower being considered. We then weight each reading’s location (longitude and latitude separately) by:
$\frac{s}{stot}$. Finally, we add the weighted longitudes and the weighted latitudes to obtain 
an estimate on the location of the cell tower. The accuracy of this algorithm grows as more readings are used. 


